Understanding Factors Contributing to DineSafe Violation Severity

### 2024-11-22 paper/paper.qmd
update package name

head(dinesafe_data) |>
  kable(
    col.names = c("Establishment Type", "Minimum Inspections", "Severity", "Action"), 
    align = "c"  # Center-align the columns
  )
```
The dataset was cleaned analyzed using the statistical programming software R [@citeR] and packages such as tidyverse [@tidy], ggplot2 [@ggplot2], kableExtra [@kable], opendatatoronto [@opendatatoronto], dplyr [@dplyr], arrow [@arrow], vgam [@vgam], testthat [@testthat], car [@car], and broom [@broom].

>>>>

head(dinesafe_data) |>
  kable(
    col.names = c("Establishment Type", "Minimum Inspections", "Severity", "Action"), 
    align = "c"  # Center-align the columns
  )
```
The dataset was cleaned analyzed using the statistical programming software R [@citeR] and packages such as tidyverse [@tidy], ggplot2 [@ggplot2], kableExtra [@kable], opendatatoronto [@opendatatoronto], dplyr [@dplyr], arrow [@arrow], VGAM [@vgam], testthat [@testthat], car [@car], and broom [@broom].
